---
title: "P8105_hw1"
output: github_document
author: "Yang Xie"
date: "2023-01-02"
---

**Load Pckages**
```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

### Problem 1
Load the penguins data set and give a short description using inline R code:
```{r}
data("penguins", package="palmerpenguins")

penguins
```

* The data set penguins has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The data set contains variables: `r colnames(penguins)`.

* The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

```{r message=FALSE, warning=FALSE}
penguins %>%
  ggplot()+
  geom_point(aes(x=bill_length_mm, y=flipper_length_mm, color=species))

ggsave('scatterplot Q1.jpg')

```



### Problem 2
```{r}
set.seed(1)

new_df <- tibble(
  vector_num = rnorm(10),
  vector_log = vector_num > 0,
  vector_char = letters[1:10],
  vector_fac = factor(c("A", "B", "c","A", "B", "c","A", "B", "c", "A"))
)

new_df
```

**Calculating the mean of variables in the dataframe**
```{r}
vnum <- pull(new_df, var = 1)
mean(vnum)

vlog <- pull(new_df, var = 2)
mean(vlog)

vchar <- pull(new_df, var = 3)
mean(vchar)

vfac <- pull(new_df, var = 4)
mean(vfac)

```

**Converting the type for non-numeric variables**
```{r}
vlog <- as.numeric(vlog)
mean(vlog)

vchar <- as.numeric(vchar)
mean(vchar)


vfac <- as.numeric(vfac)
mean(vfac)
```

* Only logical and factor typed values are converted into numeric. Character values cannot be converted.

  1. For logical values, the `as.numeric` function converts every TRUE to 1 and converts every FALSE to 0.
  1. For factor values, the `as.numeric` function converts each unique factor level to a integer begins at 1. In our case, three factor levels "A", "B", "C" are converted to 1, 2, 3 respectively.
  1. However, we can not convert character values using `as.numeric` function. All we get are NAs.


